### 2019-06-10 initial/notes.tex
figured small out
add one extra line for ref

    \item These conclusions mirror ours, if we replace $\Delta_M = B_1, \Delta_c
        = B_1 + B_2$; one may immediately see that $\Delta_c$ has the same sign
        as $\Delta_M$ in the probabilistic case, and in the $s_c > S_{0}$ case
        we have exactly $B_1, B_2 < 0$ attraction.
\end{itemize}

@@

First, let's examine our $t_{\star}$ plot (TODO add). We observe that there is a
roughly linear slope $\rd{t_{\star}}{(\Delta H)} \sim \frac{600}{s_0/2s_c}$
where $-s_0/2s_c$ is the minimum value of $H$ on the domain and so is the
maximum value for $\Delta H = H_4 - H_0$. Note that
\begin{align*}
    H(\mu, \phi; s) &= -\frac{s}{s_c}\frac{\mu^2}{2}
        + \mu \cos I - \sin I \sqrt{1 - \mu^2}\cos \phi, &
    H_4(s) &= -\sin I + \frac{s_c}{2s}\cos^2 I.
\end{align*}
While $s$ is actually a dynamical variable, it is a parameter to the 1D
Hamiltonian. Plugging these expressions ino our above expression for $\rd{K}{t}
= -\rd{(\Delta H)}{t}$, we obtain
\begin{align}
    \rd{(\Delta H)}{t} &= -\dot{\mu}^{(1)}\dot{\phi}^{(0)} - \dot{s}^{(1)}
            \rd{(\Delta H)}{s},\\
    -\rd{(\Delta H)}{(\epsilon t)} &= (1 - \mu^2)\p*{\frac{2\Omega}{s} - \mu}
            \dot{\phi}^{(0)} + 2\Omega\p*{1 + \frac{s}{2\Omega}(1 + \mu^2)}
            \s*{\frac{\mu^2}{2s_c} + \sin I + \frac{s_c}{2s^2}\cos^2 I}.
\end{align}
Now, if we evaluate far from the separatrix and for large $s$, similar to most
of our initial conditions, we obtain $\rd{(\Delta H)}{t} \approx \epsilon
\frac{s\mu^2}{s_c}\p*{1 - \mu^2 + \frac{1 + \mu^2}{2}} \sim
-\epsilon\frac{s\mu^2}{s_c}$. Comparing to our plot, we would predict that this
derivative should be close to $\frac{s/s_c}{1200}$ (assuming $s \sim s_0$
initially), so it seems like we at least have the scaling correct.

This allows for a rudimentary prediction of $t_{\star}, s_{\star}$ at separatrix
crossing; we next want to compute the separatrix crossing probabilities.

>>>>

    \item These conclusions mirror ours, if we replace $\Delta_M = B_1, \Delta_c
        = B_1 + B_2$; one may immediately see that $\Delta_c$ has the same sign
        as $\Delta_M$ in the probabilistic case, and in the $s_c > S_{0}$ case
        we have exactly $B_1, B_2 < 0$ attraction.

    \item Henrard in a later paper cites the formula $\Pr\p*{i \to j} =
        \abs*{\pd{J_j}{t} / \pd{J_i}{t}}$. This can be related to the above
        $B_i, \Delta_H$ by:
        \begin{equation}
            \Delta H = \int \pd{H}{\lambda}\dot{\lambda}\mathrm{d}t
                = \int \pd{J}{\lambda}\pd{H}{J}\dot{\lambda}\mathrm{d}t
                = 2\pi \dot{\lambda}\pd{J}{\lambda},
        \end{equation}
        where $J$ is the action variable; this is easy to see since $\pd{H}{J}$
        is just the angular velocity of the corresponding angle variable to $J$.
\end{itemize}

@@

First, let's examine our $t_{\star}$ plot (TODO add). We observe that there is a
roughly linear slope $\rd{t_{\star}}{(\Delta H)} \sim \frac{600}{s_0/2s_c}$
where $-s_0/2s_c$ is the minimum value of $H$ on the domain and so is the
maximum value for $\Delta H = H_4 - H_0$. Note that
\begin{align*}
    H(\mu, \phi; s) &= -\frac{s}{s_c}\frac{\mu^2}{2}
        + \mu \cos I - \sin I \sqrt{1 - \mu^2}\cos \phi, &
    H_4(s) &= -\sin I + \frac{s_c}{2s}\cos^2 I.
\end{align*}
While $s$ is actually a dynamical variable, it is a parameter to the 1D
Hamiltonian. Plugging these expressions ino our above expression for $\rd{K}{t}
= -\rd{(\Delta H)}{t}$, we obtain
\begin{align}
    \rd{(\Delta H)}{t} &= -\dot{\mu}^{(1)}\dot{\phi}^{(0)} - \dot{s}^{(1)}
            \rd{(\Delta H)}{s},\\
    -\rd{(\Delta H)}{(\epsilon t)} &= (1 - \mu^2)\p*{\frac{2\Omega}{s} - \mu}
            \dot{\phi}^{(0)} + 2\Omega\p*{1 + \frac{s}{2\Omega}(1 + \mu^2)}
            \s*{\frac{\mu^2}{2s_c} + \sin I + \frac{s_c}{2s^2}\cos^2 I}.
\end{align}
Now, if we evaluate far from the separatrix and for large $s$, similar to most
of our initial conditions, we approximate $\dot{\phi} \approx \frac{s_c}{s}$ and
we obtain
\begin{equation}
    \rd{(\Delta H)}{t} \approx \epsilon
        \frac{s\mu^2}{s_c}\p*{1 - \mu^2 + \frac{1 + \mu^2}{2}} \sim
        -\epsilon\frac{s\mu^2}{s_c}.
\end{equation}
Comparing to our plot, we would predict that this derivative should be close to
$\frac{s/s_c}{1200}$ (assuming $s \sim s_0$ initially), so it seems like we at
least have the scaling correct.

This allows for a rudimentary prediction of $t_{\star}, s_{\star}$ at separatrix
crossing; we next want to compute the separatrix crossing probabilities. It's
not immediately obvious whether the dissipation or adiabatic invariance term
should dominate the crossing probability or the $\Delta H$ evolution: since
$\pd{H}{s} \propto \mu^2$ but also $\dot{\phi}^{(0)} \to 0$ for much of the
trajectory, it will require some careful statistics/simulation to disentangle
the two.
